\TheTitle

### 2016-04-26 linvis.tex
Visualizing Merge Tree Section

\evantodo {
        \begin{enumerate}
                \item Add simplified abstract -- From email
                \item replace figure reference with Figure~\\ref
                \item Check captions
                \item gitk to Gitk
                \item git to Git
                \item diff to patch
                \item id to ID
        \end{enumerate}
}

@@

The verification detected no incorrect merges since 2013, two incorrect merges in
2012, and two in 2011; however, the heuristic breaks in October 15 2009 due to the
presence of \textit{foxtrot} commit, which confounds the true master branch of a
repository \footnote{See
        \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html} for a
        description of the issue}, and will not work for older merges.

@@

The goal of \tool was to simplify the  navigation of the kernel commit information, specifically by focusing on merges.
This is done by leveraging the merge-tree view of Linux to inspect how commits are merged in their way to master.

@@

In our visualizations, we leverage the Merge-Tree model described in Section~\ref{sec:mergetree}. In this model each commit is either already in Master, or is part of a tree which is rooted in the merge that merged it into Master. In that case, each
commit (whether merge or non-merge) has only one successor at most (the root of each tree has none, as it was made by Linus Torvalds directly into Master).
Commits contain the
metadata for the changes made. This metadata includes the files changed, the lines
added and removed from each file, the author, the date the commit was merged into
the merge that led to being merged into the kernel, and the date the commit was
authored, the patch, and the commit log. Merges contain less metadata, only storing
the author of the merge, the log, the commit date, and the author date, and potentially, changes necessary to address conflicts during the merge. The details
of the model are outlined in \cite{German2015}.

>>>>

\evantodo {
        \begin{enumerate}
                \item Add simplified abstract -- From email
                \item replace figure reference with Figure~\\ref
                \item Check captions
                \item gitk to Gitk
                \item git to Git
                \item diff to patch
                \item id to ID
                \item Master to master
        \end{enumerate}
}

@@

The verification detected no incorrect merges since 2013, two incorrect merges in
2012, and two in 2011; however, the heuristic breaks in October 15 2009 due to the
presence of \textit{foxtrot} commits, which confounds the true master branch of a
repository
\footnote{See \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html} for a description of the issue}, and will not work for older merges.

@@

The goal of \tool is to simplify the navigation of the kernel commit information,
specifically focusing on merges. This is done by leveraging the merge-tree view to
inspect how commits are merged on the path to the master repository.

@@

In our visualizations, we leverage the Merge-Tree model described in
Section~\ref{sec:mergetree}. In this model each commit is either already in Master,
or is part of a tree which is rooted in the merge that merged it into Master.  Each
commit, whether a merge or non-merge, has only one successor; the root of each tree
has none as it was made by Linus Torvalds directly into the master branch. Non-merge
Commits contain the metadata for the changes made. This metadata includes the files
changed, the lines added and removed from each file, the author, the date the commit
was merged into the merge that led to being merged into the kernel, the date the
commit was authored, the patch, and the commit log. Merges contain less metadata,
only storing the author of the merge, the log, the commit date, and the author date,
and potentially, changes necessary to address conflicts during the merge. The
details of the model are outlined in \cite{German2015}.
